%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[style=ieee]{biblatex}
\addbibresource{ref.bib}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large YOUYOU YANG} & Email : \href{mailto:youyou.yang@mail.mcgill.ca}{youyou.yang@mail.mcgill.ca}\\
  Github: \href{https://github.com/wppqywq}{wppqywq} & Mobile : (438)941-6404 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mcgill University}{Montréal, CA}
      {Bachelor of Science in Physics and Computer Science  %;  GPA: 3.53/4.0
      }{Aug. 2019 -- June. 2023}
      \resumeItemListStart
        \resumeItem{Relevant Coursework}
          {Quantum Mechanics, Astrophysics, Mathematical Analysis, Data Science, Machine Learning, Algorithm Design, and etc.}
          {}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BorgWarner China Technical center}{Shanghai, CN}
      {Software Development Intern}{July 2021 - August 2021}
      \resumeItemListStart
        \resumeItem{Task 1}{Develop the \textbf{communication protocol, interface and routing} in Geely Lotus automobile controller based on AutoSAR.}
        \resumeItem{Activity}{Generated interface files in C using \textbf{Python} scripting.}
        \resumeItem{Task 2}{Led upper computer modularization for "Automatic Express Car" project, implementing fixed-time and fixed-point transportation with \textbf{ROS} package on \textbf{Raspberry Pi}.}
        \resumeItem{Activity}{Wrote Linux shell scripts to regularly run Python scripts, sending signals to lower computer to run to specified coordinates on GMapping package-built graph.}
      \resumeItemListEnd

    \resumeSubheading
      {Dreame Tech}{Suzhou, CN}
      {Software Testing Intern}{May 2021 - June 2021}
      \resumeItemListStart
        \resumeItem{Task}{Test beta version of Dreame Z10 Robot Vacuum cleaner.}
        \resumeItem{Activity}{Managed firmware of the robot and control features of the Mijia app using Xmind. Captured log data with \textbf{Bash} scripts to identify and debug issues. Performed version management and problem reporting on \textbf{Jira} to assist developers in resolving bugs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {McGill ATLAS Group}{Montréal, CA}
      {Undergraduate Researcher}{May - Dec 2022}
      \resumeItemListStart
      
      \resumeItem{Sep - Dec 2022}
          {
          \textbf{Research on the parameters of Effective Field Theory Lagrangian}}
          \begin{itemize}
            \item Supervised by Prof. Brigitte Vachon and John McGowan.
            \item Estimate the parameters through maximum likelihood estimation (\textbf{MLE}) fitting method. Focused on the VBS \(W\gamma\) reaction data and analyzed the impact of systematic uncertainty on the confidence level.
          \end{itemize}
        \resumeItem{May - Aug 2022}
          {
          \textbf{Studies of gauge bosons self-interactions in high-energy proton-proton collisions}}
          \begin{itemize}
            \item Supervised by Prof. Brigitte Vachon, John McGowan and Xingguo Li.
            \item Funded by McGill Science Undergraduate Research Awards (\textbf{SURA}s).
            \item Analyzed Vector boson scattering (VBS) $W\gamma$ reaction data from the frame of Standard Model Effective Field Theory(\textbf{SMEFT}) with PyROOT library, to search for the existence of anomalous quartic gauge couplings (aQGC).
          \end{itemize}

      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Projects}

\resumeItemListStart


\resumeItem{Apr 2023}
  {\textbf{Building an Electrocardiogram (ECG) with Circuit and Arduino}}
  \resumeItemListStart
    \resumeItem{Task}{Obtained a clear and accurate ECG waveform.}
    \resumeItem{Activity}{\textbf{Hardware design} on a breadboard circuit, including a differential amplifier, a notch filter, and a low pass filter, to measure the ECG signal. }
    \resumeItem{Result}{After input signal though above circuit, 
 successfully observe the signal roughly using an \textbf{oscilloscope}, and fed it into the \textbf{Arduino} board for further visualization.}
  \resumeItemListEnd
\resumeItem{Apr 2022}
  {\textbf{Measurements of Lambda Cold Dark Matter parameters with Markov chain Monte Carlo method}}
  \resumeItemListStart
    \resumeItem{Task}{Set constraints on the basic density parameters and the Hubble's constant.}
    \resumeItem{Activity}{Fit \textbf{cosmic microwave background (CMB)} data to the standard model of the Lambda Cold Dark Matter (\(\Lambda CDM\)) using the \textbf{Markov chain Monte Carlo (MCMC)} method.}
  \resumeItemListEnd
\resumeItem{May 2022}
  {\textbf{Monte Carlo Tree Search for the Colosseum Survival game}}
  \resumeItemListStart
    \resumeItem{Task}{Developed an intelligent student agent using the \textbf{Monte Carlo Tree Search} algorithm to play the Colosseum Survival game.}
    \resumeItem{Activity}{Implemented four approaches: selection, expansion, simulation, and backpropagation.}
    \resumeItem{Result}{Successfully beat most of the random opponents and searched for the next step quickly with no significant memory usage.}
  \resumeItemListEnd

  
\resumeItemListEnd



%
%-----------EXPERIENCE-----------------
\section{Additional Experience: }
\resumeItemListStart
\resumeItem{Published Documentation}{}
    \begin{itemize}
        \item \textbf{Jul 2022: }\fullcite{McGowan:2819968}
    \end{itemize}
\resumeItem{Talks }{}
    \begin{itemize}
    \item \textbf{Aug 2022: }{Summer Undergraduate Research Showcase, McGill University: } \textit{Sensitivity studies in the search for Anomalous Quartic Gauge Couplings in proton-proton collisions at the LHC.}
    \item \textbf{Aug 2022: }{ATLAS Canada Summer Student Presentations, CERN: } \textit{Sensitivity studies in the search for Anomalous Quartic Gauge Couplings in proton-proton collisions at the LHC (same).}
    \end{itemize}
\resumeItem {Hackathon}{}
    \begin{itemize}
        \item \textbf{Jan 2022: }{Hack Mcwics 22, McGill Women in Computer Science: }{Most Practical Award-}\\
        \textit{Developing a website of Serving Size Converter.}
    \end{itemize}
\resumeItemListEnd


%
%--------SKILLS------------
\section{Skills}
 \resumeItemListStart
\resumeItem{Programming Skills}{}
    \begin{itemize}
        \item Proficient in \textbf{Python} with experience in various libraries, including \textbf{NumPy, SciPy, Pandas,} Matplotlib, Astropy, ROS, PyROOT, and Scikit-learn.
        \item Familiar with \textbf{C, Bash}, OCaml, Matlab. Have basic knowledge of \textbf{HTML+CSS}.
        \item Familiar with hardware design, experienced in \textbf{Arduino and Raspberry Pi}.
        \item Skilled in using \textbf{Linux} operating system, \textbf{Git} version control, and \LaTeX.
    \end{itemize}
\resumeItem {Language Skills}{}
    \begin{itemize}
        \item Native Mandarin speaker.
        \item English with an overall IELTS score of 6.5.
        \item French at a beginner's level.
    \end{itemize}
\resumeItemListEnd
 


%\bibliographystyle{plain}
%\bibliography{ref}

%-------------------------------------------
\end{document}
